---
title: "Homework 5"
author: "Philip Kim"
date: "11/16/2021"
output:
  github_document:
    toc: true
    toc_depth: 6
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

```{r, message = FALSE}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")
    ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

## Single city/Baltimore, MD

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n())

baltimore_test =
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

## Function

```{r}
prop_test_function = function(city_df) {
  city_summary = 
    city_df %>% 
   summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n())

city_test =
  prop.test(
  x = city_summary %>% pull(unsolved),
  n = city_summary %>% pull(n))

  return(city_test)
}

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

## Iteration across cities

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

## Plot with estimate/CI

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

# Problem 2

```{r}
files = list.files("./data/zip_data/")
```

## Function

```{r}
read_files_function = function(x) {
  
  path = str_c("./data/zip_data/", x)
  
  y = read_csv(path)
  
  return(y)
}
```

## Iterate/read in data and create new variable

```{r, message = FALSE}
study_df = 
  tibble(
    files = list.files("./data/zip_data/")) %>% 
  mutate(
    data = map(files, read_files_function))
```

## Tidy data

```{r}
tidy_study_df = 
  study_df %>% 
  separate(files, into = c("arm", "subject_id"), sep = "_") %>% 
    mutate(
      subject_id = str_remove(subject_id, ".csv"),
      arm = ifelse(arm == "con", "control", "experiment"),
      subject_id = as.numeric(subject_id),
      subject_id = ifelse(arm == "experiment", subject_id + 10, subject_id + 0),
      subject_id = as.factor(subject_id)) %>% 
  unnest(data) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation") %>% 
  mutate(
    week = as.factor(week))
```

## Spaghetti Plot

```{r}
tidy_study_df %>% 
  ggplot(aes(x = week, y = observation, color = arm)) + 
  geom_line(aes(group = subject_id)) +
  labs(
    x = "Week",
    y = "Observation Values",
    color = "Arm",
    title = "Control and Experimental Arm \nin Longitudinal Study") +
   theme(plot.title = element_text(hjust = 0.5))
```

## Comments on Differences

From the spaghetti plot, we can see that observation values between both the control and experimental arm started roughly around the same values. However, as the weeks progressed throughout the 8 week time period, the observation values of the experimental arm steadily increased whereas the values for the control arm wavered around the same values. Observation values for all participants in the experimental arm were higher than all of those in the control arm after Week 7 and 8. 

# Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>%
  janitor::clean_names()
```

## Function

```{r}
fill_in_missing = function(x) {
  
  if (is.numeric(x)) {
    
    x = replace_na(x, mean(x, na.rm = TRUE, 1))
    
  }
  
  if (is.character(x)) {
    
    x = replace_na(x, "virginica")
    
  }
  
  return(x)
}
```

## Map across columns

```{r}
iris_filled = 
  map(iris_with_missing, fill_in_missing) %>% 
  as_tibble()

sum(is.na(iris_with_missing))
sum(is.na(iris_filled))
```

